---
title: "Class Demo"
subtitle: "Quarto code demonstration"
author: "Matthew Son"
date: "2026-02-23"
format:
    html:
        toc: true
        toc-depth: 2
        toc-location: "left"
        toc-title: "Overview"
        theme: "lux"
        embed-resources: true
        output-file: "HTML_Documentation.html"
    revealjs:
        embed-resources: true
        output-file: "HTML_Slide.html"
        transition: slide
        toc: true
    docx:
        output-file: "DOCX_Documentation.docx"
    pptx:
        output-file: "PPTX_Documentation.pptx"
---

Here's some body.

# Header 1

Add some texts.

## Header 2

### Header 3

#### Header 4

##### Header 5

###### Header 6

# Code blocks

Code blocks are generated by wrapping the code with backticks.

```{r}
print("Hello world")
```

# Basic Markdowns

## Text formatting

*Italic*, **Bold**, ~~Strikeout~~, `code`.

Superscript^2^, subscript~2~

[Hyperlink](https://google.com)

Footnote[^1]

[^1]: This is the footnote information.

## Lists

-   Bullet item 1

    -   List item 2
        -   Item 3
    -   List item 4

1.  Numbered item 1
    1.  Item 2
        1.  Item 3
    2.  Item 4

## Tables

```{r}
iris |> head()
```

## Gt package

```{r}
iris |> head() |> gt::gt()
```

```{r}
#| warning: false
#|
library(tidyverse)
library(tidyquant)
stock_price <- tq_get("AAPL", from = "2023-12-01", to = "2023-12-31")
stock_price |>
  ggplot(aes(x = date, open = open, high = high, low = low, close = close)) +
  geom_candlestick() +
  labs(
    title = "AAPL Candlestick Chart, December 2023",
    x = "Date",
    y = "Price (USD)"
  ) +
  theme_bw()
```

## Chunk options

### echo: false

When you do not want to reveal the code, but output: use `echo: false`.

`echo: true` is the default behavior.

```{r}
#| echo: false
stock_price <- tq_get("AAPL", from = "2023-12-01", to = "2023-12-31")
stock_price |>
  ggplot(aes(x = date, open = open, high = high, low = low, close = close)) +
  geom_candlestick() +
  labs(
    title = "AAPL Candlestick Chart, December 2023",
    x = "Date",
    y = "Price (USD)"
  ) +
  theme_bw()
```

### warning: false

Suppress warning messages

```{r}
#| warning: false
warning("Warning!")
```

### message: false

Suppress messages (like when you load tidyverse `library(tidyverse)`)

```{r}
#| message: false
message("This is a message")

```

### include: false

If you want a code chunk to be run **silently**, but not included in the document: `include: false`

```{r}
#| include: false
my_hidden_function <- \(x) x + 2
```

```{r}
my_hidden_function(3)
```

### eval: false

If you only want to show the code, but not meant to be run: `eval: false`

```{r}
#| eval: false
print(my_hidden_function(10))
```

### error: true

```{r}
#| error: true
1 + "haha"
```


# Further resources

Check out Quarto website <https://quarto.org/docs/guide> for more information.